---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "images/"
)
```

# DataflowR

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/81863152.svg)](https://zenodo.org/badge/latestdoi/81863152)


The `DataflowR` package is used to handle streaming output and discrete grab samples collected as part of the South Florida Water Mangement District's Florida Bay Dataflow monitoring program.

## Installation

You can install DataflowR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jsta/DataflowR")
```

## Data

You can find input and output data on KNB at:

**Christopher J. Madden, Jemma Stachelek, Stephen Kelly, Michelle Blaha (2017)** Florida Bay water quality estimated by underway flow-through measurement. _KNB Data Repository_. [http://dx.doi.org/10.5063/F11R6NGR](http://dx.doi.org/10.5063/F11R6NGR)

## Function Documentation and Examples

see either:

* the vignette at `inst/doc/DataflowR.pdf`

* `??DataflowR` from the `R` console

## References

**Jemma Stachelek and Christopher J. Madden (2015)**. Application of Inverse Path Distance weighting for high density spatial mapping of coastal water quality patterns.
*International Journal of Geographical Information Science*
[preprint](http://jsta.github.io/public/stachmadden2015am.pdf) | [journal](http://dx.doi.org/10.1080/13658816.2015.1018833)

**Jemma Stachelek, Christopher J. Madden, Stephen Kelly, Michelle Blaha (submitted)**. Fine-scale relationships between phytoplankton abundance and environmental drivers in Florida Bay, USA.

